Proposal outline/notes

### 2012-06-06 docs/Jesse/Proposal/outline.tex
adding Jesse folder w/proposal outline

@@

@@

Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Discuss solution strategies (pseudo-timestep/damped Newton).

Formulate DPG for Burgers' equation as an example, showing results, then show Navier-Stokes at a broad level.

>>>>

\subsection{Optimal test functions}

\subsection{Ultra-weak variational formulation}

\subsection{Test norms}

@@

\begin{itemize}
\item Describe mathematically the issue with standard Galerkin.
\item Give proofs of robustness and numerical results (from paper)
\end{itemize}

@@

\begin{itemize}
\item Introduce nonlinear residual to measure convergence, DPG formulation for nonlinear problems. Briefly discuss solution strategies (pseudo-timestep/damped Newton). 
\item Formulate DPG for Burgers' equation as an example, show results
\item Show DPG applied to Navier-Stokes at a broad level, with results
\end{itemize}
